Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-18 paper/structureScene.tex
update Introduction, citation and "rare"=>"episodic"

An important problem in this field is the characterization of auditory scenes for the purposes of similarity estimation. One application of this is acoustic scene similarity retrieval (ASSR), where the scenes judged ``most similar'' to a given query scene are extracted from some larger dataset. This requires the auditory scenes to be represented in some way that captures their distinctive qualities. Often, this has been achieved by bag-of-frames approaches \cite{aucouturier2007bag}, which attempt to describe the auditory scene recording using summary statistics. Unfortunately, since this only captures the average structure of the scene, the approach often fails when presented scenes which are dynamic and contain rare, distinct sound events that discriminate the scene from others. Indeed, experiments in cognitive psychology suggests that this matches more closely the way that humans and other animals perceive acoustic scenes. \gl{put some Refs that are already cited if possible}

>>>>

An important problem in this field is the characterization of auditory scenes for the purposes of similarity estimation. One application of this is acoustic scene similarity retrieval (ASSR), where the scenes judged ``most similar'' to a given query scene are extracted from some larger dataset. This requires the auditory scenes to be represented in some way that captures their distinctive qualities. Often, this has been achieved by bag-of-frames approaches \cite{aucouturier2007bag}, which attempt to describe the auditory scene recording using summary statistics. Unfortunately, since this only captures the average structure of the scene, the approach often fails when presented scenes which are dynamic and contain episodic, distinct sound events that discriminate the scene from others. Indeed, experiments in cognitive psychology \cite{dubois2006cognitive} and cognitive neurosciences \cite{nelken2004processing} suggest that this matches more closely the way that humans perceive acoustic scenes.
